---
title: "Digital Humanities - Ashoka University"
author: "Team members: Navdeep Singh, Sara Singh, Soham De"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    collapsed: true
---
```{r}
library(readr)
```

### Introduction
The Partition is often described as an event that perpetuated existing religious polarities in the Indian subcontinent, and there is a tendency to speak of religious groups in context of the Partition as homogeneous and seamless entities. However, so much of Partition literature as well as post-Partition literature focuses on individuals' narratives and their own personal encounters with religion, factionalism, and nationalism. Our understanding of the Partition ceases to be as simple as mere religious disharmony, and we're shown how an individual's motivations oftentimes do not align with their larger group identity.
This phenomenon is particularly prominent in one of the short stories from Mottled Dawn, titled 'The Last Salute', in which Subedar Rab Nawaz (a Pakistani soldier) and Ram Singh (an Indian soldier) question the abstract and impersonal agenda they were fighting for after seeing that they were each others' opponents. Their own personal history of friendship and mutual support overrode their religious and national identities in the end, putting into question the nature of collective agendas and how much power they have over us. However, even their individual harmony doesn't do anything to prevent general disharmony from existing between Hindus and Muslims, and so we find that the larger group entities may still be at odds despite them being internally diverse and complex.

Based on this, our project seeks to find how religious harmony manifests in Partition literature, especially when it comes to how many people may be involved in an event relating to religious harmony. The formalized research question is: Is the theme of religious harmony in partition literature represented more frequently through interactions between distinguishable individuals or through groups of characters? This question is valuable to ask because it challenges the widely-held belief about religious groups being homogeneous and having no differentiation in motivations among the individuals that comprise them, and subsequently also provides insight on how people's behaviour changes based on group vs. individual dynamics. 

### Specific Research Question

Is the theme of religious harmony in partition literature represented more frequently through interactions between distinguishable individuals or through groups of characters?

### Queries

**Query 1:** We designed a custom Faceted Search (which we call Characters in Harmony) to filter characters appearing in events with religious harmony and observe how the numbers (pluralities) of these characters are distributed

**Query 2:** 

**(a)** We filter events for religious harmony then iterate through each character involved in these harmonious events, categorising them into single, group, male-dominated group or female-dominated group. This was done in ```R``` and ```Python```.

**(b)** We filter events for religious harmony then iterate through each character involved in these harmonious events, categorising them as above, but also across their religion as mentioned in the DB. This was done in ```R``` and ```Python```.

### Crosstabs
```{r}
crosstabs1 <- read_csv("crosstabs1.csv")
```



### Analysis
